Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambios sobre el servidor y referencias
Mejor justificación del servidor, nuevas refs, correcciones leves y
mejor respuesta al revisor

\author{P. de las Cuevas, A.M. Mora, J.J. Merelo, P. García-Sánchez, A. Fernández-Ares}
\ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
\address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
%\author{A. M. Mora}
%\ead{amorag@geneura.ugr.es}
%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}

@@

The use of a server is mainly based in the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \ref{BigData_11}. Thus, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power. These methods will include Data Mining \cite{Cios07DataMining} and Machine Learning \ref{MachineLearning_Bishop06} techniques. This server will also centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.

@@

\bibliographystyle{elsarticle-num}
\bibliography{geneura-latin1,review_muses}

>>>>

\author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\ P. García-Sánchez, A. Fernández-Ares}
\ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
\address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
%\author{A. M. Mora}
%\ead{amorag@geneura.ugr.es}
%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}

@@

The use of a server is mainly based on the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \cite{BigData_11}, since the algorithms to apply to them require high computational costs \cite{Shirkhorshidi14Review}.
Moreover, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power. These methods will include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}. This server will be also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.

@@

\bibliographystyle{elsarticle-num}
\bibliography{review_muses} %geneura-latin1
